\LARGE \bf Steering a Swarm Using Global Inputs\\ and Swarm Statistics

### 2016-08-19 journalSwarmControl/SwarmControlIJRR.tex
Convex Hall was not correct
The submitted version.

\begin{dci}
The Authors declare that there is no conflict of interest.
\end{dci}
\begin{funding}
%RULES: http://www.nsf.gov/pubs/policydocs/pappguide/nsf16001/aag_6.jsp
This work was supported by the National Science Foundation under Grant No.\ 
\href{http://nsf.gov/awardsearch/showAward?AWD_ID=1553063}{ [IIS-1553063]}.
\end{funding}
\begin{sm}
\begin{itemize}
\item Video 1:  simulation of the parameter sweeps in Fig.~\ref{fig:AutoVeryParam} with robot swarms manipulating objects.
\item Video 2: hardware experiments of object manipulation with a swarm of 100 kilobots.
\end{itemize}
\end{sm}

>>>>

\begin{dci}
The Authors declare that there is no conflict of interest.
\end{dci}
\begin{funding}
%RULES: http://www.nsf.gov/pubs/policydocs/pappguide/nsf16001/aag_6.jsp
This work was supported by the National Science Foundation under Grant No.\ 
\href{http://nsf.gov/awardsearch/showAward?AWD_ID=1553063}{ [IIS-1553063]}.
\end{funding}
\newpage
\begin{sm}
\begin{itemize}
\item Extension 1:  simulation video of the parameter sweeps in Fig.~\ref{fig:AutoVeryParam} with robot swarms manipulating objects.
\item Extension 2: hardware experiment videos of object manipulation with a swarm of 100 kilobots.
\end{itemize}
\end{sm}
